Playground for PNAS cover graphic

### 2021-11-05 cover/cover.Rmd
Fix jhu and gs

library(covidcast)
library(ggplot2)
library(dplyr)
library(purrr)
```

```{r get-data, eval = FALSE}
sources <- c("usa-facts",
             "doctor-visits",
             "fb-survey",
             "google-symptoms")

@@

```{r load-all}
# Inspect missingness: google has lots (privacy threshold)
do.call(rbind, x) %>%
  filter(geo_value %in% tolower(state.abb)) %>%
  group_by(signal, geo_value) %>%
  summarize(nas = length(dates) - n()) %>%
  ungroup() %>% group_by(signal) %>%
  filter(nas > 0)

y <- tibble(geo_value = rep(geos, each = length(dates)),
            time_value = rep(dates, length(geos)))

>>>>

library(covidcast)
library(epitools)
library(ggplot2)
library(dplyr)
library(purrr)
```

```{r get-data, eval = FALSE}
sources <- c("jhu-csse",
             "doctor-visits",
             "fb-survey",
             "google-symptoms")

@@

```{r missingness-checks}
# Inspect missingness: google has lots (privacy threshold)
do.call(rbind, x) %>%
  filter(geo_value %in% tolower(state.abb)) %>%
  group_by(signal, geo_value) %>%
  summarize(nas = length(dates) - n()) %>%
  ungroup() %>% group_by(signal) %>%
  filter(nas > 0)

# Are there any days where google is missing almost everything?
y <- tibble(geo_value = rep(geos, each = length(dates)),
            time_value = rep(dates, length(geos)))
